Linear Stochastic Approximation- Constant Step-Size and Iterate Averaging

### 2017-05-19 instance.tex
space

\textbf{Bias and Variance}: The MSE at time $t$ is bounded by a sum of two terms. The first \emph{bias} term is given by $\B=\nu_{P_U,\alpha} \,\frac{\norm{\theta_0-\ts}^2}{(t+1)^2}$, bounding how fast the initial error $\norm{\theta_0-\ts}^2$ is forgotten. 
The second \emph{variance} term is  given by $\V=\nu_{P_U,\alpha}\, \frac{\alpha^2(\sigma_A^2\norm{\ts}^2+\sigma_b^2)+\alpha (\sigma_A^2\norm{\ts})\norm{\theta_0-\ts}}{t+1} $ and captures the rate at which noise is rejected.

@@

\textbf{The lower bound} of \Cref{th:lb} shows that the upper bound of \cref{th:rate} is tight in a number of ways.
In particular, the coefficients of both the $1/t$ and $1/t^2$ terms inside $\{ \cdot \}$ are essentially matched.
Further, we also see that
the $(\rhos{P}\rhod{P})^{-1}$ appearing in $\nu_{P_u,\alpha}$ cannot be removed from the upper bound. 
Note however that there are specific examples, such as SGD for linear least-squares,
where this latter factor can in fact be avoided (for further remarks see \Cref{sec:related}).

>>>>

\textbf{Bias and Variance}: The MSE at time $t$ is bounded by a sum of two terms. The first \emph{bias} term is given by $\B=\nu \,\frac{\norm{\theta_0-\ts}^2}{(t+1)^2}$, bounding how fast the initial error $\norm{\theta_0-\ts}^2$ is forgotten. 
The second \emph{variance} term is  given by $\V=\nu\, \frac{v^2}{t+1} $ and captures the rate at which noise is rejected.

@@

\textbf{The lower bound} of \Cref{th:lb} shows that the upper bound of \cref{th:rate} is tight in a number of ways.
In particular, the coefficients of both the $1/t$ and $1/t^2$ terms inside $\{ \cdot \}$ are essentially matched.
Further, we also see that
the $(\rhos{P}\rhod{P})^{-1}$ appearing in $\nu = \nu_{P_u,\alpha}$ cannot be removed from the upper bound. 
Note however that there are specific examples, such as SGD for linear least-squares,
where this latter factor can in fact be avoided (for further remarks see \Cref{sec:related}).
